QPLIB: A Library of Quadratic Programming Instances

### 2016-07-29 QPLIB-1.0.tex
added Nick's citations

Quadratic Programming (QP) problems, where both the objective function and the constraints contain (at most) expressions in the variables of degree $2$, include a surprisingly diverse set of rather different instances. According to the fine details of the formulation, solving a QP may require employing either fundamentally combinatorial techniques, or ideas rooted in nonlinear optimization principles, or a mix of the two. In this sense, QP is likely one of the classes of problems where the collaboration between the communities interested in combinatorial and nonlinear optimization is more necessary, and potentially fruitful.

>>>>

Quadratic Programming (QP) problems, where either the objective function \cite{wiki:qp}, or the constraints \cite{wiki:qcqp}, or both contain (at most) expressions in the variables of degree $2$, include a surprisingly diverse set of rather different instances. This is not surprising, given the vast scope of practical applications of these problems, and of solution methods designed to solve them \cite{GoulToin00a}. According to the fine details of the formulation, solving a QP may require employing either fundamentally combinatorial techniques, or ideas rooted in nonlinear optimization principles, or a mix of the two. In this sense, QP is likely one of the classes of problems where the collaboration between the communities interested in combinatorial and nonlinear optimization is more necessary, and potentially fruitful.
